---
title: "Gapminder"
author: "Angela Xu"
date: "09/03/2021"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tinytex)
library(tidyverse)
library(gapminder)
library(dplyr)
data(gapminder)
```

## Introduction

In this document,we will be exploring the Gapminder dataset.

## Observations of Gapminder

### Countries with life expectancy less than 30

There are two countries with life expectancy of less than 30 in the dataset, namely:

* Afgahnistan in 1952; and

* Rwanda in 1992

    
```{r lifexplt30, echo=FALSE}

gapminder %>% filter(lifeExp<30)

```

### Countries with life expectancy greater than 81

There are five countries with life expectancy greater than 81 in the dataset. Two of the countries achieved expectancy greater than 81 twice since the year 2000. 

``` {r lifeexpgt81, echo=FALSE}

gapminder %>% filter(lifeExp>81)

```

### Life Expectancy by continent in 2007

Africa is the only continent where 75% of the countries have life expectancy of less than 70 years. 

Of the five continents, only Africa's has 75% of its countries having less than 70 years. Oceania has the highest life expectancy but that is due to it being made up of Australia and New Zealand.

```{r lifeexp2007, echo = FALSE}

a <- filter(gapminder, year == 2007)

boxplot(a$lifeExp~ a$continent, ylab = "Life Expectancy")


```

